Verifying Demonstrations

### 2018-02-20 paper/ZKPK.tex
Adds description of malicious ZKPK

\NewAlgorithm{\PKprove}{PK.\!Prove}
\NewAlgorithm{\PKverify}{PK.\!Verify}

We will rely on the Schnorr identification scheme~\cite{Schnorr}, which in its 
original form can be written as \(\PK{\alpha}{A = g^\alpha}\).
The generalized form would be \(\PK{\alpha_1, \dotsc, \alpha_n}{A = 
    \prod_{i=1}^n g_i^{\alpha_i}}\).
This could equivalently be written as
\begin{equation*}
  \PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
  \PKverify[\{g_i\}_i, q, A],
\end{equation*}
where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
verifier.
\(\PKverify\) outputs accept (1) or reject (0).
We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
We also note that
\begin{equation*}
  \PK{\alpha, \beta}{A = g^\alpha \land B = g^\beta} = \PK{\alpha}{A = g^\alpha} 
  \land \PK{\beta}{B = g^\beta},
\end{equation*}
however, the challenge \(c\) must be the same in both sub-protocols.

\begin{figure*}
  \centering
  \begin{tabular}{lcl}
    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
    &
    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
    \\
    \toprule

@@

\NewAlgorithm{\SPKprove}{SPK.\!Prove}
\NewAlgorithm{\SPKverify}{SPK.\!Verify}

For the non-interactive instance, \(\SPK{\alpha}{A = g^\alpha}{m}\), we use the 
Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
illustrated as \(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.

>>>>

\NewCryptoScheme{\Schn}{Schn}
\NewAlgorithm{\SchnProve}{\Schn.\!Prove}
\NewAlgorithm{\SchnVerify}{\Schn.\!Verify}

We will rely on the Schnorr identification scheme~\cite{Schnorr} (\Schn), which 
in its original form can be written as \(\PK{\alpha}{A = g^\alpha}\).
The generalized form would be \(\PK{\alpha_1, \dotsc, \alpha_n}{A = 
    \prod_{i=1}^n g_i^{\alpha_i}}\).
This could equivalently be written as
\begin{equation*}
  \SchnProve[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
  \SchnVerify[\{g_i\}_i, q, A],
\end{equation*}
where \(\SchnProve\) is run by the prover and \(\SchnVerify\) is run by the 
verifier.
\(\SchnVerify\) outputs accept (1) or reject (0).
We give an instance of \(\SchnProve\) and \(\SchnVerify\) in \cref{PKalgorithms}.
We also note that
\begin{equation*}
  \PK{\alpha, \beta}{A = g^\alpha \land B = g^\beta} = \PK{\alpha}{A = g^\alpha} 
  \land \PK{\beta}{B = g^\beta},
\end{equation*}
however, the challenge \(c\) must be the same in both sub-protocols.

\begin{figure*}
  \centering
  \begin{tabular}{lcl}
    \(\SchnProve[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
    &
    & \(\SchnVerify[\{g_i\}_{i=1}^n, q, A]\):
    \\
    \toprule

@@

\NewCryptoScheme{\PKscheme}{PK}
\NewAlgorithm{\PKprove}{\PKscheme.\!Prove}
\NewAlgorithm{\PKverify}{\PKscheme.\!Verify}

Schnorr (\(\Schn\)) in itself only provides honest-verifier zero-knowledge.
To achieve malicious-verifier zero-knowledge, we have to choose \(k\) (size of 
the challenge) logarithmic in the security parameter \(\lambda\) and repeat the 
protocol sufficiently many times.

\NewAlgorithm{\Prove}{Prove}
\NewAlgorithm{\Verify}{Verify}
\NewCryptoSet{\PKG}{G}
\NewCryptoSet{\PKA}{A}
\NewCryptoSet{\PKS}{S}

\begin{figure*}
  \begin{minipage}{0.49\linewidth}
    \begin{algorithmic}
      \Function{$\PKprove^S$}{$\PKG, q, A, \PKA$}
        \For{$0\leq i\leq \log\lambda$}
          \State{$\method{S}{\Prove[\PKG, q, A, \PKA][_{k = \log\lambda}]}$}
        \EndFor{}
      \EndFunction{}
    \end{algorithmic}
  \end{minipage}
  \begin{minipage}{0.49\linewidth}
    \begin{algorithmic}
      \Function{$\PKverify^S$}{$\PKG, q, A$}
        \For{$0\leq i\leq \log\lambda$}
          \State{$\method{S}{\Verify[\PKG, q, A][_{k=\log\lambda}]}$}
        \EndFor{}
      \EndFunction{}
    \end{algorithmic}
  \end{minipage}
  \caption{%
    Transforming honest-verifier zero-knowledge to malicious-verifier 
    zero-knowledge.
  }%
  \label{ZKPKalgorithms}
\end{figure*}

\NewCryptoScheme{\SSchn}{SSchn}
\NewAlgorithm{\SPKprove}{\SSchn.\!Prove}
\NewAlgorithm{\SPKverify}{\SSchn.\!Verify}

For the non-interactive instance, \(\SPK{\alpha}{A = g^\alpha}{m}\), we use the 
Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on \Schn, illustrated as 
\(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.
